%%%%%%%
% Author; Trevor Bramwell
% Date: Mon Apr 23 01:03:43 PDT 2012
%   Lab 2 writeup for CS372
%%%%%%

\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}

\usepackage{listings}
\lstset{
    breaklines=true,
    basicstyle=\footnotesize,
    escapechar=\$
}
\usepackage{chngcntr}
%\counterwithout{subsection}{section}

\usepackage{enumitem}

\renewcommand{\labelenumii}{\arabic{enumii})}

% Custom Commands
\renewcommand{\b}[1]{\textbf{#1}}
\newcommand{\q}{\textbf{Question} }
\newcommand{\ans}{\textbf{Answer} }

% Preamble
\title{Wireshark Lab 2: HTTP}
\author{
    Trevor Bramwell \\
    CS372 - Introduction to Computer Networks \\
    Professor Bechir Hamdaoui
}
\date{\today}

\begin{document}
\maketitle

\section{The Basic HTTP GET/response interation}
\begin{enumerate}
\item \q Is your browser running HTTP version 1.0 or 1.1?  What version of HTTP
    is the server running? 

\ans My browser is running HTTP 1.1, and the server is running HTTP 1.1.

\item \q What languages (if any) does your browser indicate that it can accept
    to the server? 

\ans US English and English.

\item \q What is the IP address of your computer?  Of the gaia.cs.umass.edu
    server? 

\ans My computer's IP address is \textbf{10.0.1.21}, and the
    \emph{gaia.cs.umass.edu} IP address is \textbf{128.119.245.12}.

\item \q What is the status code returned from the server to your browser?  

\ans 200

\item \q When was the HTML file that you are retrieving last modified at the
    server? 

\ans Tue, 24 Apr 2012 03:26:01 GMT

\item \q How many bytes of content are being returned to your browser? 

\ans 128 Bytes

\item \q By inspecting the raw data in the packet content window, do you see
    any headers within the data that are not displayed in the packet-listing
    window? If so, name one.

\ans No, I do not. Every header is accounted for in the raw data.
\end{enumerate}


\pagebreak
\lstinputlisting{packets/get.pkt}\pagebreak
\lstinputlisting{packets/okay.pkt}\pagebreak


% Random indent here for some reason...
\section{The HTTP CONDITIONAL GET/response interaction}
\begin{enumerate}[resume]
\item \q Inspect the contents of the first HTTP GET request from your browser
    to the server.  Do you see an ``IF-MODIFIED-SINCE'' line in the HTTP GET? 

\ans Yes. It contains the current time.

\item \q Inspect the contents of the server response. Did the server explicitly
    return the contents of the file? How can you tell? 

\ans Yes. The file is explicitly displayed below the packet.

\item \q Now inspect the contents of the second HTTP GET request from your
    browser to the server.  Do you see an ``IF-MODIFIED-SINCE:'' line in the
    HTTP GET? If so, what information follows the ``IF-MODIFIED-SINCE:''
    header? 

\ans Yes. The same date and time listed from the previous ``IF-MODIFIED-SINCE''
    header is listed.

\item \q What is the HTTP status code and phrase returned from the server in
    response to this second HTTP GET?  Did the server explicitly return the
    contents of the file? Explain.

\ans The returned response is \textbf{304 Not Modified}. The server did not
    return the contents of the file because the file had not changed since it
    was last accessed.
\end{enumerate}


\pagebreak
\lstinputlisting{packets/get2.pkt}\pagebreak
\lstinputlisting{packets/okay2.pkt}\pagebreak
\lstinputlisting{packets/get3.pkt}\pagebreak
\lstinputlisting{packets/notmodified.pkt}\pagebreak


\section{Retrieving Long Documents}
\begin{enumerate}[resume]

\item \q How many HTTP GET request messages were sent by your browser? 

\ans One HTTP GET request was sent by my browser.

\item \q How many data-containing TCP segments were needed to carry the single
    HTTP response? 

\ans 4 TCP segments were needed to carry the response.

\item \q What is the status code and phrase associated with the response to the
    HTTP GET request? 

\ans 200 OK

\item \q Are there any HTTP status lines in the transmitted data associated
    with a TCPinduced ``Continuation''? 

\ans There are no HTTP status lines in the data associated with 
    ``Continuation''
\end{enumerate}


\pagebreak
\lstinputlisting{packets/longokay.pkt}\pagebreak


\section{HTML Documents with Embeded Objects}
\begin{enumerate}[resume]
\item \q How many HTTP GET request messages were sent by your browser?  To
    which Internet addresses were these GET requests sent? 

\ans 3 seperate GET requests were sent by my browser:
    \begin{enumerate}
        \item http://gaia.cs.umass.edu/wireshark-labs/HTTP-wireshark-file4.html
        \item http://manic.cs.umass.edu/~kurose/cover\_5th\_ed.jpg
        \item http://www.pearsonhighered.com/assets/hip/us/hip\_us\_pearson\\highered/images/pearson\_logo.gif
    \end{enumerate}

\item \q Can you tell whether your browser downloaded the two images serially,
    or whether they were downloaded from the two web sites in parallel?
    Explain.

\ans The two images were downloaded serially. There is a 23 millisecond
    difference between the GET requests.

\end{enumerate}


\pagebreak
\lstinputlisting{packets/4get2.pkt}\pagebreak
\lstinputlisting{packets/4get3.pkt}\pagebreak


\section{HTTP Authentication}
\begin{enumerate}[resume]
\item \q What is the server’s response (status code and phrase) in response to
    the initial HTTP GET message from your browser? 

\ans 401 Authorization Required

\item \q When your browser’s sends the HTTP GET message for the second time,
    what new field is included in the HTTP GET message? 

\ans The Authorization field. It's value is: \\
    Basic d2lyZXNoYXJrLXN0dWRlbnRzOm5ldHdvcms=
\end{enumerate}

\pagebreak
\lstinputlisting{packets/5authorization1.pkt}\pagebreak 
\lstinputlisting{packets/5get2.pkt}\pagebreak

\end{document}
