%----
% Author: Trevor Bramwell
% Date: Mon Jun  4 21:35:04 PDT 2012
%----

\documentclass[12pt,letterpaper]{article}

\title{A Minor Inconvinence}
\author{
    Trevor Bramwell\\
    Professor Carlos Jensen\\
    CS391: Ethics in Computer Science -- MWF 1300\\
}
\date{\today}

\usepackage{url}
\usepackage{hyperref}

\hypersetup{
    colorlinks,
    citecolor=blue,
    urlcolor=black,
}

\usepackage{fullpage}
\usepackage{indentfirst}
\linespread{1}

\begin{document}
\maketitle

I grew up in the interned age. In 1998, my family got our first
computer. It came with a 56kb modem. It allowed my parents to recieve
email and my brothers and I to play games with our friends. Most of our
time on the computer was spent offline though, as dialing out for
Internet connectivity was tedious and tied up the phoneline. Every once
in a while, if my parents said it was okay because they weren't
expecting any calls, I could use the internet. Most of my time was
spent reading forum posts on Myst related topics.

After my brother picked up a book from the library on programming in
BASIC, I took more of an interest to computers. I wanted to know how
they worked, what they were made out of, how they communicated. I was
facinated by their ability to connect people not only from across the
street, but from around the world. And it was all possible because of
this silly little language called HTML. 

It wasn't long after I attempted to learn BASIC that I picked up a book
on HTML from the library. It was much easier, more concise, and just
plain made sense to my growing middle school brain. Written words on a
computer created remarkable visualizations. I was hooked. I had to learn
more.

When I first came to know and love the Internet, it was near end of the
Dot-com Bubble: A rough and marvelous time for growth on the Internet.
Since then the Interent has grown to connect a very large amount of the
United States population. Growing up with the Internet all of my life,
i was curious to find out just how addicted I had become. So for two days I went
without the Internet. 

To be honest living without the Internet wasn't that hard. Being that I
had grown up with using a 56kb modem the majority of my life I have a
fair respect for how far we have really come in terms of the speed at
which we can communicate online. Going back to using a pen and paper to
take notes during class was trivial, since I already did so. Using my
phone to text and call friends was just as trivial. But when it came to
researching information for a class, that was somewhat of a challenge.

During the first day I spent without Internet I realized that I need to
do some research for a paper I was writing in another class. Were I
able to access the Internet then, it would have been trivial to go to
Wikipedia and read an overview of the subject, before diving into the
plethora of links that eminated from the article page for a more
in-depth understanding of the topic. Instead, I had to plan ahead. Going
to the library to check out an encyclopedia containing the first letter
of my topic, and then searching, by hand, through the library card
catalog to find books relating to the subject. Thankfully the librarians
at Valley are extremely helpful and were even excited to explain how to
use a card catalog to someone new. 



Recently I deleted my Facebook
account, and I found that I caught myself typing \url{http://www.Facebook.com}, more
often than not, when I don't even have one. At random times.

The only reason my friends have a Facebook is because my friends have a
Facebook. This sounds tautological, because it is. Social media has
always been seen as this great connector, or enabler of community, but
most of the time it is wasted  with status updates of breakups, baby
facts, or cat pictures. None of the discussion revolves around anything
important, or if it does it is mainly a flame war.


\section{No Internet}
8:30am - Woke up to have a long gaming weekend. Went to look up Max
Payne 3 achievement guide online, but couldn't.

The first morning I didn't have Internet I wanted to lookup a guide for
max payne 3 achievements. I couldn't do this though. The night before I
knew when I woke up in the morning I would forget, so I disconnected my
Internet card on my Xbox and PC.i This was my first challenge, and I
failed. Two hours after getting up and realizing my Internet was turned
off, I mulled the thought over in my head.  I gave in and turned my PC
Internet back on. I went and downloaded the guide from the website and
turned my Internet right back off. This is supposed to be for for a full
48 hours, so I wouldn't turn my Internet back on until 10am the next.


Before the dance that night my girlfriend asked me to look up a recipe
for her. I responded that I couldn't because I couldn't use the Internet
for two days. She remembered and looked up the recipe herself. It was
only a minor inconvenience.


I was at a dance last weekend and a friend asked me to if I was
going to a friend's party that night. I said "What party"? They looked
at me funny. The one on Facebook, they said. Didn't you get the invite?
I had to laugh. No, I said. I don't have a Facebook anymore. Their
immediate reaction: "Why?".

\section{Internet}
\subsection{Weekday}
During a weekday I get up and go to school. Sometimes in the morning
before I go downstairs to make lunch I will play a few rounds of a
Multi-player, or Single-player game on Xbox. Then I go wait for the bus,
streaming music while I wait. On the Bus I generally keep streaming
music until I get off and walk all the way to work. At which time I
turn on my computer, login and startup IRC, and Email., and various
other websites for internal use at the OSL. I am constantly online while
I am at work either looking at email, or on IRC. During the day I have
class, so I generally leave and walk to class. Sometimes I will stream
music on my way to class. While in class I am generally completely
unplugged, unless it is a CS class where laptops are allowed.  After
class I stream music sometimes on my way back to work.  Where I plug
back in and am on IRC and email.

After work I'll walk to the bus and stream music all the way home.
(~20min). Once I am home I generally play video games, or work on my
homework. But as soon as I get home I generally make dinner,. If I am
making something simple I won't use the Internet. If it is something new
or I am being creative I will look up an recipe online. After dinner I
go to my room and play video games, or watch TV shows on Netflix until
bed.

Sometimes in the morning I wake up and, because my phone is my alarm,
check my email/Reddit/Slashdot/news.


\subsection{Non-Weekday}

On a non weekday , If I didn't stay up all day on Friday night then I
will wake up early to play some video games most of the day. Generally
depending on what game I am playing most of this will be offline. Even
though I am not playing multiplayer though, I will still be signed into
Xbox live. Most of my day will be spent playing video games. The other
day I spent about 4ish hours trying to get a game setup. I had just
downloaded the Humble Indie bundle 5. I wanted to play Limbo on Linux, but
the deb package wouldn't work, so I downloaded steam and installed it
through wine. This whole process was not easy and took me longer than it
should of because of the way wine works. I had to reference the Internet
several times to find the information I needed. I would not have of been
able to make it work without access to the Internet.

It is very obvious how reliant we are upon the Internet. There was a
satiric blog post written recently about icons on the iPhone that are
unrecognizable because we have become so detracted from technology
because everything is now online. For example on the iPhone the icon to
make a phone call is a dial-tone phone (chorded) (Back when people still
used landlines.)  The authors point was that most people don't use these
phones anymore and ironically the icon is for the device they are using
(the iPhone).

\section{Conclusion}

Having first learned HTML after being put-off by BASIC, I became
fascinated with the internet.

\subsection{Difficulties}
\subsection{How disconnect made me feel}
\subsection{Reflection on experience and feelings}

\section{Questionnaire}
\subsection{What devices do you use to access the Internet?}
The devices our household use to access the Internet are phones, game
consoles, laptops, desktops, and tablets. Daniel mainly uses the Tablet
or his iPhone. Jaymee mainly uses her tablet and iPhone. Daniel and
Jaymee both use the Wii to watch Netflix. Jacob uses his
laptop to watch Hulu. Ashlee uses her laptop and kindle fire. Courtney uses her
laptop. I use my laptop, phone, desktop and Xbox.

\subsection{What resources do you access?}
The majority of sites our household access are these:
Facebook, Reddit, Hulu, Netflix, Pintrest, Reddit, Pandora, craigslist,
eBay, wikipedia, amazon, oregonstate.edu.

\subsection{For what purpose?}
Most of the Internet usage at our house is for entertainment. A large
portion of it is probably taken up by either Netflix or Hulu streaming or
Torrenting of TV Show or Movies. After that comes gaming, as I am
constantly on the Internet playing multiplayer games. Then there is
social stuff. Facebook probably taking the cake, followed by Pintrest,
and then Reddit. After that would be Financial. Daniel spends a lot of
his time on Craigslist or eBay looking for great deals, or garage sales.

\subsection{For how long a period of time?}
Since most of the usage is taken up by entertainment or streaming, I'd
say generally between an hour to three hours. When it comes to gaming I
generally play from half an hour to around four hours.

\subsection{Bandwidth Division}
Most of the bandwidth is used for family purposes, entertainment,
gaming, social, etc. Rarely is anyone using it for 'work' with the
exception of Daniel using it for craigslist and eBay. I would say the
discretionary part happens generally later at night if at all in our
household. Of the people who live here, four of the five people are
couples.


\end{document}
