\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\title{WR222 - Essay 3\\
    Interview with Curt Pederson\\ 
    Director, OSU Open Source Lab
}

\author{
    Trevor Bramwell \\
}

\date{\today}


\begin{document}
\maketitle

The Oregon State Open Source Lab (``OSL'')

%\itemsep150pt
\begin{enumerate} 
    \item When was the OSL founded?
        In late 2003. I had worked for the Oregon State Government as the state CIO.
        Data cetner used to be for Banner. Coencided with IS paying off debt of \$6 million.
        \$1 million cut a year. \$1 million came back, \$500,000 used to fund 21 miles of fiber optic
        cable. Network Services needed more room.
        21 miles of fiber optic. 
    \item Why was the OSL Created?
        Decided to host debian and gentoo. Word of mouth spread that we were providing hosting.
        Ealy projects Firefox. Up to 200 million downloads. 160 projects hosted. Grew organically
        and strategically. Day 1 goal: provide students with real world experience.
    \item Who was involved in the founding?
        \begin{itemize}
        \item Curt Pederson
        \item Shay Dakan - Network Services director.
            Wizard behind curtain. Didn't want/care for recognition.
        \item Paul Risser - Saw www.orst.edu sign on highway.
        \item Scott and Jason were Yin and Yang. Scott was bouncing off the walls where as Jason was
        calm and collected.
        \item Scott Kveton - Hired to change domain name from www.orst.edu
            to www.oregonstate.edu.
            Former student/employee. Created Maintain. Now CEO of Urban 
            Airship.
        \item Jason McKerr - Now VP of Puppet Labs. Operating Systems, 
            Porgramatic Business.
        \end{itemize}
    \item How did the laying of dark fiber effect the creation of the OSL?
        Key. Gave a huge pipe to outside world. TDS Telecom was looking for 
        bandwidth,
        looking at us, saw amount of traffic putting out. Created 3 mirror sites for ftp.
        Chicago, New York, and Corvallis. TDS 2Gbs bandwidth no charge. Worth \$300,000 a year.
    \item There are multiple stories surrounding the history of the OSL. What
          is your version?
        Created open source lab from www.orst.edu. Academics didn't agree with osl creation.
        Felt space could have been used better. Why was osu turning resources towards outside vs.
        campus. Focused on camps benefit. Drupal deployment, helpdesk, etc. 600,000 downloads a day.
        50 some students/former employees in major positions in OS companies.
    \item Explain the financial disaster the previous CIO caused and how you handled the debt.
        Unversity didn't know \$6 million dollar deficit. Curt previous/first state CIO. Understood
        finances at the University has greatly increased. Curt previous CFO for Shnomish County, PUD.
        Had a bredth of knowledge. Mile wide, inch deep. Eliminated least used services. Nicked away.
    \item Future of OSL
       Focus is on mentoring and hosting. 
\end{enumerate}

\end{document}
