{\centering Notes\\}
\begin{description}
    \item[Thesis]
        Several events led to the creation of The Oregon State Open Source Lab 
("OSL"). Fifteen miles of dark-fiber were laid out to I-5 to help load balance
web traffic to the university, and the previous CIO cause the university's IS
department to be in debt, leading to the university moving towards open source
technologies.
    \item[Stakes]
        There is not definite understanding of how the open source lab was
created. Quotes from several different old employees conflict on this topic.
    \item[Publication]
        This essay is being written for Linux World News (lwn.net).
    \item[Alternative Cause/Effect]
        www.orst.edu domain seen by Ed Ray. Didn't want to have 'worst' domain.
This lead to a focus on web presence.
    \item[Speakers]
        Joe Brockmeier, a writer for linux.com, wrote an overview of the OSL
that includes information regarding it's history.
        Jeremy Andrews, a writer for Kerneltrap.org, blogged about Kernel
Trap's relocation to the OSL.
\end{description}

\noindent\textbf{Question}: What caused the OSL to be created?
\begin{itemize}
    \item Open Source Movement \\
        The open source movement starting with linux and progressed from there.
        It is hard to talk about open source in general without metioning the
        movement.

    \item Dark fiber \\
        ```Our CIO (Curt Pederson) chose to fund a fiber build-out to I-5 and the Open
        Source Lab. The strategic funds are seed money to get the OSL off the ground
        and we're well on our way to cost recovery.''' [Scott Kveton] (Andrews).

    \item Forced into open source due to budget \\
        ```OSU's information services group had a bit of a financial disaster 8 years
        ago; our former CIO went a little crazy writing checks, etc. After the dust
        settled, we were left with a huge debt, and increasing user base and the need
        to provide a lot more with a lot less. We had no choice but to turn to open
        source.''' [Scott Kveton] (Andrews).

    \item Worst domain name \\
        "Oregon State University president saw a sign with "www.orst.edu," and didn't
        want to have the "worst" edu domain. (Read it again.) That led OSU's president
        to get in touch with the folks running the Web site. Having drawn the attention
        of the university leadership to the Web presence, OSU paid more attention to
        hosting and eventually got into the business of hosting for open source
        projects." (Brockmeier).

    \item Gentoo hosting \\
        \tab One of the primary causes for the OSL's creation was Oregon State University's
        hosting of a Gentoo server. Gentoo is a linux distribution. ```Web services
        donated an old Dell server, and from there Gentoo just grew and grew,' says
        Lance Albertson'' (http://osuosl.org/about/stories/gentoo).
\end{itemize}
